cor

### 2023-04-10 code/analysis_code/stats/3_correlation.qmd
edits

```{r}
corrplot(b, type = "upper", order = "hclust", 
         tl.col = "black", tl.srt = 45,
         title = "Blind Oso",  mar=c(0,0,1,0)) #Adds and lowers title

>>>>

```{r, fig.width=3, fig.height=3}
corrplot(b, type = "upper", order = "hclust", 
         tl.col = "black", tl.srt = 45,
         title = "Blind Oso",  mar=c(0,0,1,0)) #Adds and lowers title
